---
title: 'Sanfrancisco at summer 2014: August has more Criminal at Weekend'
author: "Q"
date: "Sunday, November 29, 2015"
output: html_document
---

This is a practice analysis for coursera lesson: Communicating Data Science Result.

Prepare data:
```{r}
library(ggplot2)
setwd('C:/Users/QQ/Documents/GitHub/datasci/datasci_course_materials/assignment6')
san_data <- read.csv('sanfrancisco_incidents_summer_2014.csv')
san_data$FTime <- paste(san_data$Date, san_data$Time)
san_data$FTime <- strptime(san_data$FTime, '%m/%d/%Y %H:%M')
san_data$Month <- format(san_data$FTime, format='%m')
san_data$Hour <- format(san_data$FTime, format='%H')
head(san_data)
```

Following plot shows that weekend of August has more criminal incident than other time period. Possibly the weather is hot and people has more time at weekend.

```{r}
ggplot(san_data) + geom_bar(aes(x=DayOfWeek,fill=Month),position='dodge') + labs(y='Criminal Counts',title='Criminal at Month$WeekDay')

```

Following plot shows that there are more criminal incident especially at midday. Possibly it's because the temperature is especially high.

```{r}
ggplot(san_data) + geom_bar(aes(x=Hour,fill=Month)) + labs(y='Criminal Counts',title='Criminal at Month$WeekDay')
```
